%-------------------------
% Resume in Latex
% Author : Jonathan Quespaz
% Based on: Wilmer Gonzalez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% Import core configurations
\input{config/packages}     % Package imports and basic setup
\input{config/commands}     % Resume-specific commands
\input{config/language}     % Language settings
\input{config/theme}        % Theme settings
\input{config/colors}       % Color themes
\input{config/links}        % Link styling and commands
\input{config/references}   % Document references

% Set language and theme
\Englishtrue  % Comment for Spanish
\Darktrue     % Comment for light theme

% DOCUMENT MAIN
\begin{document}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{https://www.linkedin.com/in/jonathanquespaz/}
        {\Large Jonathan David Quespaz Sanchez}} & \href{https://github.com/JonathanDQS}
        {\faicon{github} \color{urlcolor} JonathanDQS} \\
    \href{mailto:jonathanquespaz2007@gmail.com}{jonathanquespaz2007@gmail.com} & \faicon{code} Angular, .NET \\
    \textsl{\small \latestVersion} & \textsl{\small \otherThemeRef,}
    \textsl{\small \languageVersion}
\end{tabular*}

% Section modified for English and Spanish support line by line, the following
% sections have 2 versions 1 for English and 1 for Spanish
% EXPERIENCE
\section{\EngOrSp{Experience}{Experiencia}}
	\headingListStart
	\heading
      		{Fibramax}{\EngOrSp{Sangolqui}{Sangolquí}, Ecuador}
      		{\EngOrSp{Senior Software Developer}{Desarrollador de Software Senior}}{\EngOrSp{November 2024}{Noviembre 2024} -- \EngOrSp{Present}{Presente}}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{Co-leading the development of an in-house ERP system to streamline operations and support business growth. My responsibilities include the optimization of backend development with Django, PostgreSQL, and Python, as well as frontend implementation using React. Additionally, driving the adoption of DevOps practices by implementing Docker and GitLab to enhance deployment automation, scalability, and system efficiency within an Agile environment.}
	        {Coliderando el desarrollo de un sistema ERP interno para optimizar las operaciones y respaldar el crecimiento del negocio. Mis responsabilidades incluyen la optimización del desarrollo backend con Django, PostgreSQL y Python, así como la implementación del frontend utilizando React. Además, impulsando la adopción de prácticas DevOps mediante la implementación de Docker y GitLab para mejorar la automatización del despliegue, la escalabilidad y la eficiencia del sistema dentro de un entorno Agile.}}
        \detailListEnd
    \heading
      		{Netby IT Consulting}{Quito, Ecuador}
      		{\EngOrSp{Software Developer}{Desarrollador de Software}}{\EngOrSp{June 2024}{Junio 2024} -- \EngOrSp{November 2024}{Noviembre 2024}}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{At Confiamed, a leading prepaid medicine insurance company, I worked extensively with Azure DevOps microservices to optimize and enhance backend operations. My responsibilities included bug fixing, implementing new functionalities, and ensuring system efficiency. I primarily focused on backend development using .NET, Entity Framework (EF), and SQL Server, all within an Agile environment.}
	        {En Confiamed, una empresa líder en seguros de medicina prepagada, trabajé extensamente con microservicios de Azure DevOps para optimizar y mejorar las operaciones del backend. Mis responsabilidades incluyeron la corrección de errores, la implementación de nuevas funcionalidades y la garantía de la eficiencia del sistema. Me centré principalmente en el desarrollo backend utilizando .NET, Entity Framework (EF) y SQL Server, todo dentro de un entorno Ágil.}}
        \detailListEnd
	\heading
      		{Sedemi}{Sangolqu\EngOrSp
      		{i}{í}, Ecuador}
      		{Senior Software Developer Analyst}{Mayo 2023 -- \EngOrSp{May 2024}{Mayo 2024}}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{Developed and implemented new Angular applications, adhering to approved functional documents and designs. I proactively suggested and coded enhancements to improve usability and compatibility. Additionally, I contributed to backend API development using the .NET framework and various design patterns. These applications were integral to supporting the migration to a new ERP system.}
	        {Desarrollé e implementé nuevas aplicaciones en Angular, siguiendo documentos funcionales y diseños aprobados. Proactivamente sugerí y codifiqué mejoras para optimizar la usabilidad y la compatibilidad. Además, contribuí al desarrollo de APIs en el backend utilizando el framework .NET y varios patrones de diseño. Estas aplicaciones fueron fundamentales para apoyar la migración a un nuevo sistema ERP.}}
	      	
    	      \resumeItem{\EngOrSp
            {The applications were specifically developed to support the Project Management department, Collections department, and the Production Plant for Construction.}{Las aplicaciones fueron desarrolladas específicamente para apoyar al departamento de Gestión de Proyectos, al departamento de Cobranza, y a la Planta de Producción para Construcción.}}
	    \detailListEnd
		\heading
      		{WebCreek}{Quito, Ecuador}
      		{Software Engineer I}{Feb 2021 -- \EngOrSp{Feb 2022}{Feb 2022}}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{Designed and developed modules for an existing application focused on accounting logic, utilizing .NET for backend development and Angular for the frontend.}
	        {Diseñé y desarrollé módulos para una aplicación existente enfocada en lógica contable, utilizando .NET para el desarrollo backend y Angular para el frontend.}}
	      	\resumeItem{\EngOrSp
	      	{Modified a web application to enhance responsiveness, utilizing SASS and integrating third-party libraries. I refactored the majority of styles and coordinated efforts to implement new modules, ensuring consistency and delivering an improved user experience.}
	      	{Modifiqué una aplicación web para mejorar la capacidad de respuesta, utilizando SASS e integrando bibliotecas de terceros. Refactoricé la mayoría de los estilos y coordiné esfuerzos para implementar nuevos módulos, asegurando la consistencia y brindando una mejor experiencia de usuario.}}
		\detailListEnd
		\heading
      		{WebCreek}{Quito, Ecuador}
      		{Software Engineer - Internship}{\EngOrSp{Aug}{Ago} 2020 -- Feb 2021}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{Collaborated in a multicultural team to develop reports using the DevExpress Reporting tool. Gained experience with the .NET framework and Angular, managing requests and creating a visually appealing interface.}
	      	{Colaboré en un equipo multicultural para desarrollar informes utilizando la herramienta DevExpress Reporting. Adquirí experiencia con el framework .NET y Angular, gestionando solicitudes y creando una interfaz visualmente atractiva.}}
		\detailListEnd
		\heading
      		{Disanort (\EngOrSp
      		{Family Business}{Negocio Familiar})}{Sangolqu\EngOrSp
      		{i}{í}, Ecuador}
      		{\EngOrSp
      		{English, Physics and Math Tutor}
      		{Tutor de Inglés, Física y Matemática}}
      		{2017 -- \EngOrSp{Present}{Presente}}
    	\detailListStart
	      	\resumeItem{\EngOrSp
	      	{Taught and provided academic support to students across middle school, high school, and their first years of higher education.}
	      	{Enseñé y brindé apoyo académico a estudiantes de secundaria, preparatoria y primeros años de educación superior.}}
		    \resumeItem{\EngOrSp
		    {Currently tutoring students when required}
		    {Actualmente desempeñandome como tutor personal según se
		    requiera}}
		\detailListEnd
	\headingListEnd
% ---

% EDUCATION
\EngOrSp{\section{Education}
  \headingListStart
    \heading
		{Escuela Politecnica Nacional EPN}{Quito, Ecuador}
		{MSc in Software}{May 2020 -- May 2024}
        \detailListStart
	    	\resumeItem{Summa Cum Laude}
		    \resumeItem{{\MasterThesis}}
	    \detailListEnd
    \heading
	    {The University of Manchester}{Manchester, UK}
	    {BEng in Computer Systems Engineering}{2016 -- 2019}
	    \detailListStart
	    	\resumeItem{First Class}
		    \resumeItem{{\certificateOfHE} and {\academicT}}
	    \detailListEnd
    % \heading
	% 	{INTO Manchester}{Manchester, UK}
	% 	{IFY - International Foundation Year}{2015 -- 2016}
	% 	\detailListStart
	% 		\resumeItem{Results: Further Maths - A*, Maths - A*, Physics - A*,
	% 		EAP - A}
	% 	\detailListEnd
	%\heading
		%{Unidad Educativa Santa Ana}{Sangolqui, Ecuador}
		%{High School Degree in Sciences}{2008 -- 2014}
		%\detailListStart
			%\resumeItem{Result: 9,76/10}
		%\detailListEnd
  \headingListEnd}
  {\section{Educación}
  \headingListStart
    \heading
		{Escuela Politécnica Nacional EPN}{Quito, Ecuador}
		{Maestría en Software}{Mayo 2020 -- Mayo 2024}
        \detailListStart
	    	\resumeItem{Summa Cum Laude}
		    \resumeItem{{\MasterThesis}}
	    \detailListEnd
    \heading
	    {The University of Manchester}{Manchester, UK}
	    {Ingeniería en Sistemas Computacionales}{2016 -- 2019}
	    \detailListStart
	    	\resumeItem{Primera clase}
		    \resumeItem{{\certificateOfHE} y {\academicT}}
	    \detailListEnd
	% \heading
	% 	{INTO Manchester}{Manchester, UK}
	% 	{Año de preparación propedéutico internacional}{2015 -- 2016}
	% 	\detailListStart
	% 		\resumeItem{Resultados: Matemática Avanzada - A*, Matemática - A*,
	% 		Física - A*, Inglés para propósitos académicos - A}
	% 	\detailListEnd
	%\heading
		%{Unidad Educativa Santa Ana}{Sangolquí, Ecuador}
		%{Bachillerato en Ciencias -- BGU}{2008 -- 2014}
		%\detailListStart
			%\resumeItem{Resultado: 9,76/10}
		%\detailListEnd
  \headingListEnd}
% ---

% CERTIFICATIONS
\EngOrSp{\section{Certifications}
  \headingListStart
		\heading
			{Coursera}{MOOC}
			\TSOper{Issued May -- 2023}
		\heading
			{Coursera}{MOOC}
			\TSVars{Issued May -- 2023}
		\heading
			{Coursera}{MOOC}
			\IntroBash{Issued May -- 2023}
    \heading
      {Coursera}{MOOC}
      \MOOC{Issued Jul -- 2020}
    \heading
      {Udemy}{MOOC}
      \UdemyMOOC{Issued Jun -- 2021}
  \headingListEnd}
  {\section{Certificaciones}
  \headingListStart
		\heading
			{Coursera}{MOOC}
			\TSOper{Otorgado May -- 2023}
		\heading
			{Coursera}{MOOC}
			\TSVars{Otorgado May -- 2023}
		\heading
			{Coursera}{MOOC}
			\IntroBash{Otorgado May -- 2023}
    \heading
      {Coursera}{MOOC}
      \MOOC{Otorgado Jul -- 2020}
    \heading
      {Udemy}{MOOC}
      \UdemyMOOC{Otorgado Jun -- 2021}
  \headingListEnd}

% ---

% PROJECTS
%\EngOrSp{\section{Projects}
 % \headingListStart
  %  \resumeSubItem{\textbf{HelpMeOut:} Web app aimed to students. Managed the backend with PHP and databases with MySQL and phpmyadmin.}

	%\resumeSubItem{\textbf{Stendhal:} Developed, tested and deployed a feature in an open source MORPG.}

	%\resumeSubItem{\ParcOS}

  %\headingListEnd}
  %{\section{Proyectos}
  %\headingListStart
   % \resumeSubItem{\textbf{HelpMeOut:} Aplicación Web enfocada a estudiantes. Encargado del backend con PHP y base de datos con MySQL.}

	%\resumeSubItem{\textbf{Stendhal:} Desarrollo, prueba y lanzamiento de un componente en un juego MORPG.}

	%\resumeSubItem{\ParcOS}

  %\headingListEnd}
% ---

% PERSONAL PUBLICATIONS
\section{\EngOrSp{Publications}{Publicaciones}}

  \headingListStart
    \resumeSubItem{\href{https://www.ijiet.org/show-207-2760-1.html}{A Closer Look at MOOC Accessibility: Comparing Local and Global Platforms with WCAG 3.0 in Mind}}

  \headingListEnd
% ---

% PROGRAMMING SKILLS
\EngOrSp{\section{Programming Languages Experience}
	\headingListStart
		\resumeSubItem{\textbf{C:} Mainly used for the implementation of well-known algorithms and optimization techniques. Heuristics, dynamic programming, Dijkstra, are a few examples}

		%\resumeSubItem{\textbf{Assembly ARM:} Developed a primitive OS and used it for the implementation of microcontroller's routines}

		\resumeSubItem{\textbf{Java:} Used for multi-threading performance analysis, simple GUI development, Android applications, distributed systems simulations, Spring Framework web apps development}

		\resumeSubItem{\textbf{Matlab:} Implemented machine learning algorithms such as linear regression, knn, k-means and Naive Bayes}

		%\resumeSubItem{\textbf{PHP:} Backend management of a web page, fairly simple and straight forward implementation}

		\resumeSubItem{\textbf{SQL:} Analysed case studies based on the Relational and Enhanced Relational models, implementing them in an Oracle server}

		%\resumeSubItem{\textbf{Verilog:} HDL used to build a wide range of units ranging from traffic light controllers to more complex systems such as a video display unit}

		\resumeSubItem{\textbf{Python:} Analysed signals in the frequency domain, encoded and decoded multimedia files using different approaches, worked on error detection and correction aimed to mobile systems}

		% \resumeSubItem{\textbf{JavaScript:} Experience acquired in order to use the Google Maps API and	Geo-location services in order to facilitate the use of the Spring Framework in web apps}

		% \resumeSubItem{\textbf{C$\sharp$:} Backend handling of requests in a web application. Mostly worked on DB updates, filter data optimally before processing to pass it to the frontend, and report generation using DevExpress}

	\headingListEnd}
	{\section{Experiencia en Lenguajes de programaci\'on}
	\headingListStart
		\resumeSubItem{\textbf{C:} Principalmente usado para la implementación de
		algoritmos conocidos y técnicas de optimización. Métodos heurísticos,
		programación dinámica y Dijkstra son algunos ejemplos.}

		%\resumeSubItem{\textbf{Assembly ARM:} Desarrollo de un sistema operativo primitivo además de rutinas para microcontroladores}

		\resumeSubItem{\textbf{Java:} Usado para analizar el rendimiento de
		programas multithread, desarrollo de interfaces gráficas simples,
		aplicaciones Android, simulaciones de sistemas distribuidos y desarrollo
		de aplicaciones web usando Spring Framework}

		\resumeSubItem{\textbf{Matlab:} Programación de algoritmos de aprendizaje
		automático como regresión lineal, knn, k-means y Naive Bayes}

		%\resumeSubItem{\textbf{PHP:} Manejo de backend de una página web}

		\resumeSubItem{\textbf{SQL:} Análisis de casos de estudio basados en el
		modelo relacional y modelo relacional mejorado, implementándolos en un
		servidor Oracle}

		%\resumeSubItem{\textbf{Verilog:} Construcción de una variedad de unidades desde un controlador de luces de semáforo hasta una pantalla de visualización de video.}

		\resumeSubItem{\textbf{Python:} Análisis de señales en el dominio de
		frecuencias, codificación y decodificación de archivos multimedia usando
		enfoques variados, también aprendizaje de detección y corrección de
		errores en el contexto de sistemas móviles}

		% \resumeSubItem{\textbf{JavaScript:} Experiencia adquirida para usar la
		% API de Google Maps y sus servicios de Geolocalización para facilitar su
		% uso con Spring Framework}

		% \resumeSubItem{\textbf{C$\sharp$:} Manejo de peticiones al backend en una
		% aplicación web. Lo más usual era actualización de records en bases de
		% datos, filtrado óptimo previo al procesamiento y paso al frontend y la
		% generación de reportes usando DevExpress}

	\headingListEnd}
% ---
% PROJECTS
\EngOrSp{\section{Additional Info}
\headingListStart
\resumeSubItem{\textbf{Languages:} Spanish -- Native speaker, English -- \Ctwo}

\resumeSubItem{\textbf{Qualifications:} Driver's license, \PADI}

\headingListEnd}
{\section{Información Adicional}
\headingListStart
\resumeSubItem{\textbf{Lenguajes:} Español -- Hablante nativo, Ingl\'es -- \Ctwo}

\resumeSubItem{\textbf{Cualificaciones:} Licencia de conducir Tipo B, \PADI}

\headingListEnd}
% ---

\end{document}